\rule{\textwidth}{4pt}\\[1em] \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payoff Approximation in Discrete Space}\\[1em] \rule{\textwidth}{2pt}

### 2025-02-19 latex/article.tex
weighted

>>>>

\begin{figure}[htbp]
\centering
\input{weighted_loss.tex}
\caption{Weighted Error Method Performance}
\label{fig:weighted}
\end{figure}

Figure~\ref{fig:weighted} illustrates the performance of the weighted error method, 
which places greater emphasis on accurately approximating regions with larger payoff 
values. This approach is particularly useful when the economic significance of errors 
varies with the magnitude of the target payoff, providing a more practical solution 
for trading applications.
